{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
placed rules in miniboxes
explained first execution rule

@@

\todo{Place proofstrees into one line with minipages and beautify me}
\begin{figure}
\begin{align*}
\inferrule{P[i] \in SeqIns \\ se, i \vdash_{seq} s \Rightarrow t}
{se, i \vdash s \Rightarrow t}
\end{align*}

\begin{align*}
\inferrule{P[i] = \mathtt{start} pc \\ se(i) \leq se(pc)}
{se, i \vdash s \Rightarrow s}
\end{align*}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

>>>>

The scheduler is allow to pick a new thread after every transition of $\leadsto_{seq}$. The
intuition of the first rule is, that the scheduler picks a new thread $ctid$ which is at
program point $i$. This program point maps to an sequential instruction. The exection of
this instruction leads to a local state $\sigma$ and a global memory $\mu$. If these conditions
are met and instruction $i$ was not the last instruction (i.e. $\sigma.pc \neq \mathtt{exit}$),
then the concurent transition can be made. In this transition the concurrent state is updated
according to the results of the sequential execution and the thread id and security level of $i$
is recorded in the history.

@@

\todo{beautify me}
\begin{figure}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] \in SeqIns \\ se, i \vdash_{seq} s \Rightarrow t}
{se, i \vdash s \Rightarrow t}
\end{align*}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] = \mathtt{start} pc \\ se(i) \leq se(pc)}
{se, i \vdash s \Rightarrow s}
\end{align*}
\end{minipage}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}
